Towards an Ecological Trait-data Standard

### 2017-11-13 manuscript/manuscript.Rmd
update figure 2

---
title: "Towards an Ecological Trait-data Standard"
author:
- name: Florian D. Schneider \footnotemark[1] \footnotemark[2]
- name: Malte Jochum \footnotemark[4] 
- name: Gaetane LeProvost \footnotemark[2] 
- name: Andreas Ostrowski \footnotemark[5] 
- name: Caterina Penone \footnotemark[4] 
- name: Nadja K. Simons \footnotemark[6] 
csl: amnat.csl
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    template: pretty.template
    keep_tex: yes
  html_document:
    fig_caption: yes
    fig_width: 4
    highlight: null
    keep_md: yes
    theme: united
  word_document:
    fig_caption: yes
    fig_width: 6
bibliography: div05.bib
---

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth, angle=0]{figures/fig2.png}
\caption{Formats used for trait datasets. Identifiers relate the measurement to other layers of information on the specimen, the taxon or the trait measured. a) taxon-level traits are often published as a compiled species $\times$ traits matrix; b) measured data report measurements on the specimen-level, i.e. one physical occurrence of a taxon; c) a measurement long-table is a well defined and tidy data format, reporting one single measurement per row and relating it to an occurrence and taxon via unambiguous identifiers.   }

>>>>

---
title: "Towards an Ecological Trait-data Standard"
author:
- name: Florian D. Schneider \footnotemark[1] \footnotemark[2]
- name: Malte Jochum \footnotemark[4]
- name: Gaetane LeProvost \footnotemark[2]
- name: Andreas Ostrowski \footnotemark[5]
- name: Caterina Penone \footnotemark[4]
- name: Nadja K. Simons \footnotemark[6]
csl: amnat.csl
output:
  word_document:
    fig_caption: yes
    fig_width: 6
  pdf_document:
    fig_caption: yes
    fig_crop: no
    keep_tex: yes
    template: pretty.template
  html_document:
    fig_caption: yes
    fig_width: 4
    highlight: null
    keep_md: yes
    theme: united
bibliography: div05.bib
---

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth, angle=0]{figures/fig2.png}
\caption{Formats used for trait datasets.  a) taxon-level trait data compiled from literature or aggregated from measurements are often published as a compiled species $\times$ traits matrix; b) wide-tables report measurements on the specimen-level, i.e. one physical occurrence of a taxon; c) a measurement long-table is a well defined and tidy data format, reporting one single measurement per row and relating it to a trait definition and taxon via unambiguous identifiers. Additional identifiers relate each row to other layers of information on d) the specimen (occurrence) or e) the origin or confidence on the reported measurement or fact.}
